mixchar

### 2018-08-03 manuscript/manuscript.Rnw
Add authors

\section*{Paper Authors}
1. Windecker, Saras M. \\
2. Vesk, Peter A. \\
3. Catford, Jane A. \\
4. Golding, Nick.

\section*{Paper Author Roles and Affiliations}
1. PhD Candidate, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
2. Associate Professor, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
3. Assistant Professor, Biological Sciences, University of Southampton, Highfield Campus, Southampton SO17 1BJ, UK \\
4. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia

>>>>

\section*{Paper Authors}
1. Windecker, Saras M. \\
2. Vesk, Peter A. \\
3. Trevathan-Tackett, Stacey M. \\
4. Catford, Jane A. \\
5. Macreadie, Peter I. \\
4. Golding, Nick.

\section*{Paper Author Roles and Affiliations}
1. PhD Candidate, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
2. Associate Professor, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
3. Research Fellow, Centre for Integrative Ecology, School of Life and Environmental Sciences, Deakin University, Burwood Campus, Burwood VIC 3124, Australia \\
4. Assistant Professor, Biological Sciences, University of Southampton, Highfield Campus, Southampton SO17 1BJ, UK \\
5. Associate Professor, Centre for Integrative Ecology, School of Life and Environmental Sciences, Deakin University, Burwood Campus, Burwood VIC 3124, Australia \\
6. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia
